Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-12-13 manuscript/Suppl_material/supplementary.Rmd
update ms. and new suppl-material folder

# Supplementary material

@@

Popular link functions include the logit link and the complementary log-log link, as shown in Figure 14.

@@

```{r plot-link-functions, fig.cap = "(ref:descr-plot14-caption)", out.width='80%'}
knitr::include_graphics("../Tutorial_2_Bayesian/figures/linkfunctions.png")
```

@@

To gain a sense of what prior *logit* values would approximate a uniform distribution on the probability scale, @kurzAppliedLongitudinalDataAnalysis2023 simulated a large number of draws from the Uniform(0,1) distribution, converted those draws to the log-odds metric, and fitted a Student's t distribution. Row C in Figure 15 shows that using a t-distribution with 7.61 degrees of freedom and a scale parameter of 1.57 as a prior on the logit scale, approximates a uniform distribution on the probability scale. According to @kurzAppliedLongitudinalDataAnalysis2023, such a prior might be a good prior for the intercept(s) in a logit-hazard model, while the N(0,1) prior in row D might be a good prior for the non-intercept parameters in a logit-hazard model, as it gently regularizes p towards .5 (i.e., a zero effect on the logit scale).

@@

```{r plot-priors, fig.cap = "(ref:descr-plot15-caption)", out.width='80%'}
knitr::include_graphics("../Tutorial_2_Bayesian/figures/plot_of_priors.png")
```

@@

>>>>

---
title             : no
shorttitle        : "A tutorial on hazard analysis"
bibliography      : ["extrareferences2.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

```{r setup, include = FALSE}
pkg <- c("papaja", "citr", "tidyverse", "RColorBrewer", "patchwork")

lapply(pkg, library, character.only = TRUE)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r plot-settings}
## theme settings for ggplot
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)

## Set the amount of dodge in figures
pd <- position_dodge(0.7)
pd2 <- position_dodge(1)
```

```{r global-chunk-settings}
## set the figure options
knitr::opts_chunk$set(fig.pos='H', out.extra = '', out.height = "67%",
                      fig.align = "center") # initial version
```

<!-- the below two lines directly change the default Figure and Table naming to Supplementary -->

<!-- see here for more details - https://stackoverflow.com/questions/47173279/internationalization-r-knitr-figure-caption-label -->

\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\tablename}{Supplemetentary Table}

# Supplemental Material

@@

Popular link functions include the logit link and the complementary log-log link, as shown in Supplementary Figure 1.

@@

```{r plot-link-functions, fig.cap = "(ref:descr-plot14-caption)", out.width='80%'}
knitr::include_graphics("../../Tutorial_2_Bayesian/figures/linkfunctions.png")
```

@@

To gain a sense of what prior *logit* values would approximate a uniform distribution on the probability scale, @kurzAppliedLongitudinalDataAnalysis2023 simulated a large number of draws from the Uniform(0,1) distribution, converted those draws to the log-odds metric, and fitted a Student's t distribution. Row C in Supplementary Figure 2 shows that using a t-distribution with 7.61 degrees of freedom and a scale parameter of 1.57 as a prior on the logit scale, approximates a uniform distribution on the probability scale. According to @kurzAppliedLongitudinalDataAnalysis2023, such a prior might be a good prior for the intercept(s) in a logit-hazard model, while the N(0,1) prior in row D might be a good prior for the non-intercept parameters in a logit-hazard model, as it gently regularizes p towards .5 (i.e., a zero effect on the logit scale).

@@

```{r plot-priors, fig.cap = "(ref:descr-plot15-caption)", out.width='80%'}
knitr::include_graphics("../../Tutorial_2_Bayesian/figures/plot_of_priors.png")
```

@@

# References
